partial: An R Package for Creating Partial Dependence Plots

### 2016-08-09 manuscript/greenwell.tex
minor edits

Next, we plot the partial dependence of \code{Species} on both \code{Petal.Width} and \code{Petal.Length} for each of the three classes. The result is displayed in Figure~\ref{fig:partial_iris}.
\begin{example}
pd <- NULL
for (i in 1:3) {
  tmp <- partial(iris.svm, pred.var = c("Petal.Width", "Petal.Length"),
                 which.class = i, train = iris)
  pd <- rbind(pd, cbind(tmp, Species = levels(iris$Species)[i]))
}
lattice::levelplot(y ~ Petal.Width * Petal.Length | Species, data = pd)
\end{example}

@@

In this paper, we showed how to construct PDPs for various types of black box models in R using the \pkg{partial} package. We discussed similar approaches in other packages. Ways to avoid extrpolation and high excecution times were demonstrated via examples. There is a bright future for \pkg{partial} in terms of growth. For example, we would like to include the ability to construct PDPs for various types of survival models (e.g. conditional random forests with censored response).

>>>>

Next, we plot the partial dependence of \code{Species} on both \code{Petal.Width} and \code{Petal.Length} for each of the three classes. The result is displayed in Figure~\ref{fig:partial_iris}. Note that we had to supply the original training data to \code{partial} through the \code{train} option. This is necessary for fitted model objects that don't store a copy of the training data (e.g., model fitting functions that don't rely on a formula method).
\begin{example}
pd <- NULL
for (i in 1:3) {
  tmp <- partial(iris.svm, pred.var = c("Petal.Width", "Petal.Length"),
                 which.class = i, train = iris)
  pd <- rbind(pd, cbind(tmp, Species = levels(iris$Species)[i]))
}
lattice::levelplot(y ~ Petal.Width * Petal.Length | Species, data = pd)
\end{example}

@@

In this paper, we showed how to construct PDPs for various types of black box models in R using the \pkg{partial} package. We briefly discussed related approaches in other packages as well. Ways to avoid extrpolation and high excecution times were demonstrated via examples. There is a bright future for \pkg{partial} in terms of growth. For example, we would like to include the ability to construct PDPs for various types of survival models (e.g. conditional random forests with censored response).
